### 2018-08-03 Sections/abstract.tex
Worked on security essay. Added Zixin.
minor

\begin{abstract}
\newpage
The desire to share and unite remote digital assets motivated the development of the classical internet, the enabler of the entire 21st century economy and our modern way of life. As we enter the quantum era, it is to be expected there will be a similar demand for networking quantum assets, motivating a \textit{global quantum internet} for bringing together the world's quantum resources, leveraging off their exponential trajectory in capability. We present models for quantum networking, how they might be applied in the future, and the implications they will have. Socially, economically, politically and geo-strategically, the upcoming era of quantum supremacy will be as significant for the 21st century as the transistor was for the 20th.
\\[4pt]
The inherently different scaling in the computational power of quantum computers fundamentally changes the dynamics of how they will operate in the future. Given their high expected initial cost, a client/server model for outsourcing computation will be essential for enabling the accessibility and proliferation of this technology, and ensuring its economic viability. We therefore anticipate the emergence of \textit{cloud quantum computing}, a model for outsourcing quantum computations to the network. We argue that economic efficiency will mandate that all future quantum computers be united into a single global \textit{virtual quantum computer}, offering exponentially more power to all network participants than if they were to keep their resources to themselves. This model for the allocation of computational resources is uniquely quantum, with no classical analogue, completely altering the economic landscape for the future of computation.
\\[4pt]
Given the sensitivity of much of the data to which future quantum computers are going to foreseeably be applied, protocols for encrypted quantum computation will be essential -- the outsourcing of computations that neither an eavesdropper nor even the server performing the computation can spy on. This will enable new models for the commercialisation and proliferation of quantum technologies, unlike any existing models for classical computing.
\\[4pt]
We argue that the quantum internet will not create a system of winners and losers, but will rather be of benefit to all of humanity, rich and poor alike, to an even greater extent than the classical internet. It is therefore essential that it be imminently established and pursued.
\\[4pt]
While this work is only an early step in a rapidly developing field, still in its infancy, the central concepts we present will be highly relevant to future developments, laying the groundwork for this blossoming field.
\\[4pt]
We present both original ideas, as well as an extensive review of relevant and related background material. The work is divided into technical sections (requiring only a basic knowledge of the notation of quantum mechanics), for those interested in mathematical details, as well as extensive, entirely non-technical sections for the less technically inclined.
\\[4pt]
We target this work very broadly at quantum and classical computer scientists, classical computer systems, software and network engineers, physicists, economists, artists, musicians, and those just generally curious about the future of quantum technologies and what they might bring to humanity.
\\[4pt]
\textit{--- Ad astra per alas fideles. Scientia potentia est.}

\includegraphics[width=0.55\columnwidth]{sketch_cover}
\newpage
\end{abstract}

>>>>

\begin{abstract}
\newpage
\dropcap{T}{he} desire to share and unite remote digital assets motivated the development of the classical internet, the enabler of the entire 21st century economy and our modern way of life. As we enter the quantum era, it is to be expected there will be a similar demand for networking quantum assets, motivating a \textit{global quantum internet} for bringing together the world's quantum resources, leveraging off their exponential trajectory in capability. We present models for quantum networking, how they might be applied in the future, and the implications they will have. Socially, economically, politically and geo-strategically, the upcoming era of quantum supremacy will be as significant for the 21st century as the transistor was for the 20th.
\\[4pt]
The inherently different scaling in the computational power of quantum computers fundamentally changes the dynamics of how they will operate in the future. Given their high expected initial cost, a client/server model for outsourcing computation will be essential for enabling the accessibility and proliferation of this technology, and ensuring its economic viability. We therefore anticipate the emergence of \textit{cloud quantum computing}, a model for outsourcing quantum computations to the network. We argue that economic efficiency will mandate that all future quantum computers be united into a single global \textit{virtual quantum computer}, offering exponentially more power to all network participants than if they were to keep their resources to themselves. This model for the allocation of computational resources is uniquely quantum, with no classical analogue, completely altering the economic landscape for the future of computation.
\\[4pt]
Given the sensitivity of much of the data to which future quantum computers are going to foreseeably be applied, protocols for encrypted quantum computation will be essential -- the outsourcing of computations that neither an eavesdropper nor even the server performing the computation can spy on. This will enable new models for the commercialisation and proliferation of quantum technologies, unlike any existing models for classical computing.
\\[4pt]
We argue that the quantum internet will not create a system of winners and losers, but will rather be of benefit to all of humanity, rich and poor alike, to an even greater extent than the classical internet. It is therefore essential that it be imminently established and pursued.
\\[4pt]
While this work is only an early step in a rapidly developing field, still in its infancy, the central concepts we present will be highly relevant to future developments, laying the groundwork for this blossoming field.
\\[4pt]
We present both original ideas, as well as an extensive review of relevant and related background material. The work is divided into technical sections (requiring only a basic knowledge of the notation of quantum mechanics), for those interested in mathematical details, as well as extensive, entirely non-technical sections for the less technically inclined.
\\[4pt]
We target this work very broadly at quantum and classical computer scientists, classical computer systems, software and network engineers, physicists, economists, artists, musicians, and those just generally curious about the future of quantum technologies and what they might bring to humanity.
\\[4pt]
\latinquote{Carpe futurum. Ad astra per alas fideles. Scientia potentia est.}

\if 1\sketchesmode
	\includegraphics[width=0.55\linewidth]{sketch_cover}
\fi

\newpage
\end{abstract}

### 2018-08-03 Sections/network_topologies.tex
minor

The complete graph, denoted $K_{|V|}$, is a $|V|$-vertex graph where every vertex has an undirected link to every other. From a networking point of view, this can be regarded as the extremity of exclusive-use P2P networking, whereby every node has a direct link with every other. Thus, any sender can directly communicate with any receiver, via a dedicated direct channel, with no need to utilise any indirect routes. This topology has the favourable property that although any node can communicate with any other, by exclusively utilising direct P2P links we achieve several benefits:
\begin{itemize}
\item Packet collisions can be mitigated entirely, thereby maximising network efficiency.
\item Competition for the use of links can be eliminated, minimising congestion and the need for buffering (i.e quantum memory).
\item Network costs can typically be minimised, as every route only traverses a single link, and there will be no accumulation of costs.
\item The network has maximal route redundancy, making it the most tolerant against link failures\footnote{To disconnect a given node from the network, all \mbox{$|V|-1$} links emanating from it must be broken, otherwise redundant routes to the remainder of the network will exist.}.
\item A trivial \textsc{First-Come First-Served} routing strategy can be employed, eliminating the need for any dynamic or computationally complex strategies.
\item If the network allows indirect routes to be established, the maximal redundancy of the topology also maximises the ability for routing strategies to engage in load-balancing across routes.
\item In the special case of a symmetric complete graph, whereby all edge weights are approximately equal, the shortest path between any two nodes is trivially the P2P link between them, and no complex scheduling algorithms are required.
\end{itemize}
However, these highly desirable benefits come at the expense of requiring the most elaborate and expensive network, with maximal interconnectedness.

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\mathrm{start} - x_\mathrm{finish}| + |y_\mathrm{start} - y_\mathrm{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance.

@@

The worst-case number of edges that must be traversed to reach any vertex from any other is $2d$, which implies that accumulated cost metrics scale as at most \mbox{$c=O(|V|)$}. Trees are the most frugal graphs in their number of edges, which are fixed at \mbox{$|E|=|V|-1$}, irrespective of the branching parameters, since because the graph is strictly acyclic, every addition of an edge requires the addition of exactly a single vertex. This makes tree graphs the cheapest to construct in terms of physical resource usage.

@@

A variation on any graph, $G$, is to instead have a randomised implementation of it, whereby each of the possible edges \mbox{$e\in E$} or vertices \mbox{$v\in V$} occurs with some probability \mbox{$0\leq p_\mathrm{perc}\leq 1$}. These are referred to as \textit{edge percolation} and \textit{site percolation} graphs respectively.

@@

%The average number of links emanating from any node is \mbox{$e_\mathrm{av} = (|V|-1)p_\mathrm{edge}$}.

>>>>

The complete graph, denoted $K_{|V|}$, is a $|V|$-vertex graph where every vertex has an undirected link to every other. From a networking point of view, this can be regarded as the extremity of exclusive-use P2P networking, whereby every node has a direct link with every other. Thus, any sender can directly communicate with any receiver, via a dedicated direct channel, with no need to utilise any indirect routes. This topology has the favourable property that although any node can communicate with any other, by exclusively utilising direct P2P links we achieve several benefits:
\begin{itemize}
\item Packet collisions can be mitigated entirely, thereby maximising network efficiency.
\item Competition for the use of links can be eliminated, minimising congestion and the need for buffering (i.e quantum memory).
\item Network costs can typically be minimised, as every route only traverses a single link, and there will be no accumulation of costs.
\item The network has maximal route redundancy, making it the most tolerant against link failures\footnote{To disconnect a given node $v$ from the network, all $|v|$ links emanating from it must be broken, otherwise redundant routes to the remainder of the network will exist.}.
\item A trivial \textsc{First-Come First-Served} routing strategy can be employed, eliminating the need for any dynamic or computationally complex strategies.
\item If the network allows indirect routes to be established, the maximal redundancy of the topology also maximises the ability for routing strategies to engage in load-balancing across routes.
\item In the special case of a symmetric complete graph, whereby all edge weights are approximately equal, the shortest path between any two nodes is trivially the P2P link between them, and no complex scheduling algorithms are required.
\end{itemize}
However, these highly desirable benefits come at the expense of requiring the most elaborate and expensive network, with maximal interconnectedness.

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\mathrm{start} - x_\mathrm{finish}| + |y_\mathrm{start} - y_\mathrm{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance. Thus, the maximum number of hops between any two points in the network is \mbox{$O(m+n)$}.

@@

The worst-case number of edges that must be traversed to reach any vertex from any other is \mbox{$2d=O(\mathrm{log}|V|)$}, which implies that accumulated cost metrics scale as \mbox{$c=O(\mathrm{log}|V|)$}. Trees are the most frugal graphs in their number of edges, which are fixed at \mbox{$|E|=|V|-1$}, irrespective of the branching parameters, since because the graph is strictly acyclic, every addition of an edge requires the addition of exactly a single vertex. This makes tree graphs the cheapest to construct in terms of physical resource usage.

@@

A variation on any graph, $G$, is to instead have a randomised implementation of it, whereby each of the possible edges \mbox{$e\in E$} or vertices \mbox{$v\in V$} occurs with some probability \mbox{$0\leq p_\mathrm{perc}\leq 1$}. These are referred to as \textit{edge percolation} and \textit{site percolation} graphs respectively. For any given graph, its associated percolation graph has average vertex and edge counts,
\begin{align}
|E|_\mathrm{av} &= p_\mathrm{edge}\cdot |E|,\nonumber\\
|V|_\mathrm{av} &= p_\mathrm{vertex}\cdot |V|,
\end{align}
for edge and vertex percolations respectively.

@@
